### 2017-07-18 sheets/talk-11/sheet-11.tex
Fix typos, notation and extend some explantations

  We can decompose $\sigma'$ as $\sigma' = (p_\Gamma, q_\Gamma) \circ \sigma' =
  (p_\Gamma \circ \sigma', q_\Gamma\sigma') = (\sigma \circ p', M)$, where $M
  \equiv q_\Gamma\sigma'$ (of type $\Delta' \vdash A(\sigma \circ p')
  ~\text{type}$). Let $\delta$ be morphism
  \[
    \delta \equiv (p', M) \from \Delta' \to \Delta.A\sigma
  \]
  which is suitable since $p_\Delta \circ \delta = p'$ and
  \[
    (\sigma \circ p_\Delta, q) \circ \delta =
    (\sigma \circ p_\Delta \circ \delta, q\delta) =
    (\sigma \circ p', q_\Gamma\sigma') =
    (p_\Gamma \circ \sigma', q_\Gamma\sigma') =
    (p_\Gamma, q_\Gamma) \circ \sigma' =
    \sigma'
  \]

  For uniqueness assume morphism $\delta' \from \Delta' \to \Delta.A\sigma$
  such that $(\sigma \circ p_\Delta, q) \circ \delta' = \sigma'$ and $p_\Delta
  \circ \sigma' = p'$. As before we have $\delta' = (p_\Delta \circ \delta',
  q\delta') = (p', N)$ where $N \equiv q\delta'$. The following equalities
  hold:
  \[
    N = q\delta' = q_\Gamma(\sigma \circ p_\Delta \circ \delta', q\delta') = q_\Gamma((\sigma \circ p_\Delta, q) \circ \delta') = q_\Gamma\delta' = M
  \]
  and therefore $\delta' = \delta$.
\end{answer}

@@

  \emph{Hint}: Read section $1.2.1$ in Huber's thesis for the general case.
\end{exercise}
\begin{answer}
  For a CwF $(\cat{C}, F), I, J \in ob(\cat{C}), f \from J \to I$ we the elements of $\mathit{Ty}(\Gamma)$:
  \[
    (A \to A)\rho = \{w | w_f \in A(\rho f), u \in A(\rho f)\} = \{\lambda I f u.u\}
  \]
  And required equalities hold trivially for any $g \from K \to J$: $((\lambda
  I f u.u)_f u) g = (\lambda I f u.u)_{fg} (ug)$.

  Then we give a term by the following equation:
  \[
    ((\lambda q) \rho)_f u = q(\rho f, u) = u
  \]
\end{answer}

@@

  \[
    \inference[List-E]{
      \Gamma, l: \mathbf{List_A} \vdash B ~\text{type}\\
      \Gamma \vdash H_{nil} : B[nil_A/l]\\
      \Gamma, a : A, l : \mathbf{List_A}, x: B \vdash H_{cons} : B[Cons(a, l)/l]\\
      \Gamma \vdash l : \mathbf{List_A}
    }{\Gamma \vdash R^{\mathbf{List_A}}_{[l: \mathbf{List_A}]B}(H_{nil}, [a : A, l: \mathbf{List_A}, x : B] H_{cons}, l) : B[l/l]}
  \]

@@

  \[
    \inference[List-C-cons]{
      \Gamma \vdash R^{\mathbf{List_A}}_{[l: \mathbf{List_A}]B}(H_{nil}, [a : A, l: \mathbf{List_A}, x: B] H_{cons}, Cons(a, l)) : B[Cons(a, l)/l]
    }{\Gamma \vdash R^{\mathbf{List_A}}_{[l: \mathbf{List_A}]B}(H_{nil}, [a : A, l: \mathbf{List_A}, x: B] H_{cons}, Cons(a, l)) = D}
  \]
  where $D = H_{cons}[a/a, l/l, R^{\mathbf{List_A}}_{[l: \mathbf{List_A}]B}(H_{nil}, [a : A, l: \mathbf{List_A}, x : B] H_{cons}, l)/x] : B[Cons(a, l)/l]$.

@@

  And finally the $\mathit{Vec_A(n)}$ type:
  \[
    \mathit{Vec_A(n)} \vcentcolon= \Sigma l: \mathbf{List_A}. Id_\mathbb{N}(n, \mathit{Length}(l))
  \]
\end{answer}

>>>>

  We can decompose $\sigma'$ as $\sigma' = (p_\Gamma, q_\Gamma) \circ \sigma' =
  (p_\Gamma \circ \sigma', q_\Gamma\sigma') = (\sigma \circ p', M)$, where $M
  \equiv q_\Gamma\sigma'$ (of type $\Delta' \vdash A(\sigma \circ p')
  ~\text{type}$). Let $\delta$ be the morphism
  \[
    \delta \equiv (p', M) \from \Delta' \to \Delta.A\sigma
  \]
  which is suitable since $p_\Delta \circ \delta = p'$ and
  \[
    (\sigma \circ p_\Delta, q) \circ \delta =
    (\sigma \circ p_\Delta \circ \delta, q\delta) =
    (\sigma \circ p', q_\Gamma\sigma') =
    (p_\Gamma \circ \sigma', q_\Gamma\sigma') =
    (p_\Gamma, q_\Gamma) \circ \sigma' =
    \sigma'
  \]

  For uniqueness assume morphism $\delta' \from \Delta' \to \Delta.A\sigma$
  such that $(\sigma \circ p_\Delta, q) \circ \delta' = \sigma'$ and $p_\Delta
  \circ \sigma' = p'$. As before we have $\delta' = (p_\Delta \circ \delta',
  q\delta') = (p', N)$ where $N \equiv q\delta'$. The following equalities
  hold:
  \[
    N = q\delta' = q_\Gamma(\sigma \circ p_\Delta \circ \delta', q\delta') = q_\Gamma((\sigma \circ p_\Delta, q) \circ \delta') = q_\Gamma\sigma' = M
  \]
  and therefore $\delta' = \delta$.
\end{answer}

@@

  \emph{Hint}: Read section $1.2.1$ in Huber's thesis for the general case.
\end{exercise}
\begin{answer}
  For a CwF $(\cat{C}, F), I, J \in ob(\cat{C}), f \from J \to I$ we give the
  element of $\mathit{Ty}(\Gamma)$ corresponding to the type $A \to A$:
  \[
    (A \to A)\rho = \{w | w_f \in A(\rho f), u \in A(\rho f)\} = \{\lambda I f u.u\}
  \]
  The required equalities hold trivially for any $g \from K \to J$, $((\lambda
  I f u.u)_f u) g = (\lambda I f u.u)_{fg} (ug)$.

  $\Gamma, x : A \vdash x : A$ corresponds to $q$ in the model. Thus $\Gamma
  \vdash \lambda x.x : A -> A$ corresponds to $\lambda q$ being defined as
  follows:
  \[
    ((\lambda q) \rho)_f u = q(\rho f, u) = u
  \]
\end{answer}

@@

  \[
    \inference[List-E]{
      \Gamma, l: \mathbf{List_A} \vdash B ~\text{type}\\
      \Gamma \vdash H_{nil} : B[nil_A/l]\\
      \Gamma, a : A, l : \mathbf{List_A}, x: B \vdash H_{cons} : B[Cons(a, l)/l]\\
      \Gamma \vdash M : \mathbf{List_A}
    }{\Gamma \vdash R^{\mathbf{List_A}}_{[l: \mathbf{List_A}]B}(H_{nil}, [a : A, l: \mathbf{List_A}, x : B] H_{cons}, M) : B[M/l]}
  \]

@@

  \[
    \inference[List-C-cons]{
      \Gamma \vdash R^{\mathbf{List_A}}_{[l: \mathbf{List_A}]B}(H_{nil}, [a : A, l: \mathbf{List_A}, x: B] H_{cons}, Cons(N, M)) : B[Cons(N, M)/l]
    }{\Gamma \vdash R^{\mathbf{List_A}}_{[l: \mathbf{List_A}]B}(H_{nil}, [a : A, l: \mathbf{List_A}, x: B] H_{cons}, Cons(N, M)) = D}
  \]
  where $D = H_{cons}[N/a, M/l, R^{\mathbf{List_A}}_{[l: \mathbf{List_A}]B}(H_{nil}, [a : A, l: \mathbf{List_A}, x : B] H_{cons}, M)/x] : B[Cons(N, M)/l]$.

@@

  And finally the $\mathit{Vec_A(n)}$ type:
  \[
    \mathit{Vec_A(n)} \vcentcolon= \Sigma l: \mathbf{List_A}. Id_\mathbb{N}(n, \mathit{Length}(l))
  \]

  Note that it is not the only way to define $\mathit{Vec_A(n)}$, as one could
  define it with the type formers analogously to our type $\mathit{List_A}$.
\end{answer}
